Supporting information

### 2019-04-01 EAshiklomanovSA2.Rmd
Fix author list in supplement 2
Formatting fixes for submission

---
title: Supporting information
author:
  - >
    Alexey N. Shiklomanov,
    Elizabeth M. Cowdery,
    Michael Bahn,
    Chaeho Byun,
    Joseph Craine,
    Andrés Gonzalez-Melo,
    Steven Jansen,
    Koen Kramer,
    Vanessa Minden,
    Ülo Niinemets,
    Yusuke Onoda,
    Enio Egon Sosinski,
    Nadejda A. Soudzilovskaia,
    Michael C. Dietze
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

correlation_range_cap <- paste(
  "Relationship between pairwise correlation strength and data range for each PFT.",
  "In each pair of sub-panels, the left panel is relationship between pairwise correlation",
  "and the range of the variable on the x axis",
  "while the right panel is the relationship between pairwise correlation",
  "and the y variable",
  "(For instance, in the two-panel figure in row 1 column 2,",
  "the left panel is the SLA-leaf lifespan correlation as a function of the range of SLA",
  "and the right panel is the same correlation as a function of the range of leaf lifespan).",
  "Data range is expressed as the difference between the 2.5% and 97.5% quantiles of each normalized trait (i.e. $\\frac{X}{E[X]}$).",
  "Grey shading is the 95% confidence interval around a local regression (LOESS).",
  "Upper triangle is area-normalized values, and lower triangle is mass-normalized values."
)
```

>>>>

---
title: Supporting information
author:
  - >
    Alexey N. Shiklomanov,
    Elizabeth M. Cowdery,
    Michael Bahn,
    Chaeho Byun,
    Steven Jansen,
    Koen Kramer,
    Vanessa Minden,
    Ülo Niinemets,
    Yusuke Onoda,
    Nadejda A. Soudzilovskaia,
    Michael C. Dietze
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

correlation_range_cap <- paste(
  "Relationship between pairwise correlation strength and data range for each PFT.",
  "In each pair of sub-panels, the top panel is relationship between pairwise correlation",
  "and the range of the variable on the x axis",
  "while the bottom panel is the relationship between pairwise correlation",
  "and the y variable",
  "(For instance, in the two-panel figure in row 1 column 2,",
  "the top panel is the SLA-leaf lifespan correlation as a function of the range of SLA",
  "and the bottom panel is the same correlation as a function of the range of leaf lifespan).",
  "Data range is expressed as the difference between the 2.5% and 97.5% quantiles of each normalized trait (i.e. $\\frac{X}{E[X]}$).",
  "Grey shading is the 95% confidence interval around a local regression (LOESS).",
  "Upper triangle is area-normalized values, and lower triangle is mass-normalized values."
)
```
